---
title: "CMT package notes"
author: "Mike Sandiford"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CMT package notes}
  %\VignetteEngine{knitr::rmarkdown}
  \VignetteEncoding{UTF-8}
---
```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
```

## CMT package

The cmt package  assembles, updates and process gCMT ndk files for analysis in R

### Package organisation

`ndk` files are downloaded  stored in package directory data as RDS files in the paackage `data` directroy.

In order update the files a disk local directory need to identified (and possibly created) for download the `.ndk` files from gcMT.

The  function `cmt::set_cmt_sys` is used to set and or retrieve the environment variable that holds the directory which is stored in the file `bash/.cmtdir` in the cmt package.


```{r environment_set}
cmt::set_cmt_sys()
```

note that set's the `R_CMT_HOME` evironrment variable 
```{r environment_get}
Sys.getenv("R_CMT_HOME")
```

### updating the RDS files

`cmt::update_cmt()` is called to update the  ndk files to the diretcory specified by `Sys.getenv("R_CMT_HOME")` 
```{r update_cmt, eval=FALSE}
cmt::update_cmt()
```

this also merges the ndk files and converts them to a `.fwf` format wiuth 1 recor on each line (ndk fiuels have 1 reecord spread across five lines). the rsulatnt fiels are 

`cmt::cmt2rds()` converts the `.fwf` files to `.RDS`  and isntall them in the cmt package data directopry ready for access.



<!-- ## Including Plots -->

<!-- You can also embed plots, for example: -->

<!-- ```{r pressure, echo=FALSE} -->
<!-- plot(pressure) -->
<!-- ``` -->

<!-- Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot. -->
