---
title: "CMT package notes"
author: "Mike Sandiford"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CMT package notes}
  %\VignetteEngine{knitr::rmarkdown}
  \VignetteEncoding{UTF-8}
---
```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
```

## CMT package

The cmt package  assembles, updates and process gCMT ndk files for analysis in R

### package organsiation

ndk  files are downloaded  stored in package directory data as RDS fiels.

to up date the fiels we neemd to creatae a local directory and dowlonad the .ndk files from gcMT.

the  function set_cmt_sys is used to set and or retrieve the envuronment variable that holds the directory which si stored in the file "bash/.cmtdir" in the CMT package 
```{r cars}
cmt::set_cmt_sys()
```

<!-- ## Including Plots -->

<!-- You can also embed plots, for example: -->

<!-- ```{r pressure, echo=FALSE} -->
<!-- plot(pressure) -->
<!-- ``` -->

<!-- Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot. -->
